Supplementary Analyses

### 2023-02-05 drafting_supplementary_analysis.Rmd
added plots

P_R <- x$`Puerto Rico`
P_R <- 
  `rownames<-`(
    `colnames<-`(
      as.data.frame(
        rbind(
          # c("mean F","SD F","mean M", "SD M", "t","df","p","d")
          # ,
          c(
            P_R$moral_identity_internal[which(P_R$sex3=="male")]
            ,"-"
            ,P_R$moral_identity_internal[which(P_R$sex3=="female")]
            ,"-"
            ,"-"
            ,"-"
            ,"-"
            ,"-"))),
      c("mean F","SD F","mean M", "SD M", "t","df","p","d"))
    ,c("Peurto Rico"))

@@

@@

@@

P_R <- x$`Puerto Rico`
P_R <- 
  `rownames<-`(
    `colnames<-`(
      as.data.frame(
        rbind(
          # c("mean F","SD F","mean M", "SD M", "t","df","p","d")
          # ,
          c(
            P_R$moral_identity_symbolic[which(P_R$sex3=="male")]
            ,"-"
            ,P_R$moral_identity_symbolic[which(P_R$sex3=="female")]
            ,"-"
            ,"-"
            ,"-"
            ,"-"
            ,"-"))),
      c("mean F","SD F","mean M", "SD M", "t","df","p","d"))
    ,c("Peurto Rico"))

@@

# Overview

# Testing for Country Effects

# start building the model
## first test if country should be included

# no country
interceptOnly <-gls(moral_identity_internal ~ 1
                    , data = df
                    , method = "ML"
                    , na.action = na.exclude)
summary(interceptOnly)

# country included
randomInterceptOnly <-lme(moral_identity_internal ~ 1
                          , data = df
                          , random = ~1|country
                          , method = "ML"
                          , na.action = na.exclude)
summary(randomInterceptOnly)

LL_d <- logLik(interceptOnly)*-2 - logLik(randomInterceptOnly)*-2
aov <- anova(interceptOnly, randomInterceptOnly)
country_p <- aov$`p-value`[2]

@@

Initial testing revealed that for Internalization, allowing intercepts to vary with Country significantly improved the predictive power of the model $\chi$^2^(`r round(aov$df[2]-aov$df[1], digits=2)`) = `r round(aov$L.Ratio[2],digits=2)`, *p* `r paste(p_report(country_p))`.

```{r}
test <- 
  do.call(
    rbind,
    tapply(df$moral_identity_internal, df$ISO3, descriptives)
    )

descriptives(df$moral_identity_internal)

test[order(-test$mean), ]
country_order <- rownames(test[order(-test$mean), ])
```

```{r, internalizationCountry, include=TRUE}
apa_table(
  test
  , caption = "Internalization basic descriptives by Country")
```

```{r}
# https://www.r-bloggers.com/2019/03/all-around-the-world-maps-and-flags-in-r/
df$flag_location <- rep(-1)

test1 <- test[order(-test$mean), ]
test1$country1 <- rownames(test1)
test1$position <- c(11:(10+length(test1$country1)))
test1$ISO3 <- test1$country1
test1$position_country <- paste0(test1$position,test1$country1)
df1 <- left_join(df, test1, by = "ISO3")
```

g <- ggplot(df1,aes(x=position_country,y=moral_identity_internal))+
  #geom_violin() +
  stat_summary(fun=mean, geom="point", shape=23, size=2)+
  geom_boxplot(width=0.1, outlier.shape = NA)+
  xlab("Country")+
  ylab("Internalization")+
  geom_jitter(shape=16, position=position_jitter(0.15), size=.1, color="dark grey")+
  geom_axis_flags(breaks = df1$position_country,
                   labels = df1$ISO3,
                   country_icons = df1$ISO3,
                   axis = "x",
                    width = 20,
                   # lineheight = 2,
                   # fontface = "bold"
  )
```

<div class=superbigimage>
```{r, meanInternalization,include=TRUE,fig.width=20,fig.height=6}
suppressWarnings(print(g))

</div>
## Symbolization

```{r}
# 
# # start building the model
# ## first test if country should be included
# 
# # no country
# interceptOnly <-gls(moral_identity_symbolic ~ 1
#                     , data = df
#                     , method = "ML"
#                     , na.action = na.exclude)
# summary(interceptOnly)
# 
# # country included
# randomInterceptOnly <-lme(moral_identity_symbolic ~ 1
#                           , data = df
#                           , random = ~1|country
#                           , method = "ML"
#                           , na.action = na.exclude)
# summary(randomInterceptOnly)
# 
# LL_d <- logLik(interceptOnly)*-2 - logLik(randomInterceptOnly)*-2
# aov <- anova(interceptOnly, randomInterceptOnly)
# country_p <- aov$`p-value`[2]

Initial testing revealed that for Symbolization, allowing intercepts to vary with Country significantly improved the predictive power of the model $\chi$^2^(`r round(aov$df[2]-aov$df[1], digits=2)`) = `r round(aov$L.Ratio[2],digits=2)`, *p* `r paste(p_report(country_p))`.

```{r}
test <- 
  do.call(
    rbind,
    tapply(df$moral_identity_symbolic, df$ISO3, descriptives)
    )

descriptives(df$moral_identity_symbolic)

test[order(-test$mean), ]
country_order <- rownames(test[order(-test$mean), ])
```

```{r, symbolizationCountry, include=TRUE}
apa_table(
  test
  , caption = "Symbolization basic descriptives by Country")
```

```{r}
# https://www.r-bloggers.com/2019/03/all-around-the-world-maps-and-flags-in-r/
df$flag_location <- rep(-1)

test1 <- test[order(-test$mean), ]
test1$country1 <- rownames(test1)
test1$position <- c(11:(10+length(test1$country1)))
test1$ISO3 <- test1$country1
test1$position_country <- paste0(test1$position,test1$country1)
df1 <- left_join(df, test1, by = "ISO3")
```

g <- ggplot(df1,aes(x=position_country,y=moral_identity_symbolic))+
  #geom_violin() +
  stat_summary(fun=mean, geom="point", shape=23, size=2)+
  geom_boxplot(width=0.1, outlier.shape = NA)+
  xlab("Country")+
  ylab("Symbolization")+
  geom_jitter(shape=16, position=position_jitter(0.15), size=.1, color="dark grey")+
  geom_axis_flags(breaks = df1$position_country,
                   labels = df1$ISO3,
                   country_icons = df1$ISO3,
                   axis = "x",
                    width = 20,
                   # lineheight = 2,
                   # fontface = "bold"
  )
```

<div class=superbigimage>
```{r, meanSymbolization,include=TRUE,fig.width=20,fig.height=6}
suppressWarnings(print(g))

</div>

# Gender Differences

```{r}
test <- 
  do.call(
    rbind,
    tapply(df$moral_identity_internal, df$sex3, descriptives)
    )

descriptives(df$moral_identity_internal)

test[order(-test$mean), ]
country_order <- rownames(test[order(-test$mean), ])
```

```{r, internalizationgender, include=TRUE}
apa_table(
  test
  , caption = "Internalization basic descriptives by Gender")
```

```{r}
df1 <- df
g <- ggplot(df1,aes(x=sex3,y=moral_identity_internal))+
  geom_violin() +
  #ggforce::geom_sina(size=.01)+
  stat_summary(fun=mean, geom="point", shape=23, size=2)+
  geom_boxplot(width=0.1, outlier.shape = NA)+
  xlab("Gender")+
  ylab("Internalization")+  
  geom_jitter(shape=16, position=position_jitter(height = .5, width = .45), size=.01, color="dark grey")

g
```

```{r, meanInternalizationGender,include=TRUE}
suppressWarnings(print(g))

```{r}
test <- 
  do.call(
    rbind,
    tapply(df$moral_identity_symbolic, df$sex3, descriptives)
    )

descriptives(df$moral_identity_symbolic)

test[order(-test$mean), ]
country_order <- rownames(test[order(-test$mean), ])
```

```{r, symbolizationgender, include=TRUE}
apa_table(
  test
  , caption = "Symbolization basic descriptives by Gender")
```

```{r}
df1 <- df
g <- ggplot(df1,aes(x=sex3,y=moral_identity_symbolic))+
  geom_violin() +
  #ggforce::geom_sina(size=.01)+
  stat_summary(fun=mean, geom="point", shape=23, size=2)+
  geom_boxplot(width=0.1, outlier.shape = NA)+
  xlab("Gender")+
  ylab("Symbolization")+  
  geom_jitter(shape=16, position=position_jitter(height = .5, width = .45), size=.01, color="dark grey")

g
```

```{r, meanSymbolizationGender,include=TRUE}
suppressWarnings(print(g))

# Predictors (Individual Level Only)

## Internalization
```{r}
x <- df[which(df$sex3=="male"|df$sex3=="female"),]
x$sex3 <- droplevels(x$sex3)

```{r, include=TRUE, echo=TRUE}

model1 <- lmerTest::lmer(moral_identity_internal ~
                    sex3
                  * age
                  + (1|country)
                , data = x
                , contrasts = list(sex3 = contr.sum, valence = contr.sum )
            )
summary(model1)
anova(model1)

## Symbolization
```{r}
x <- df[which(df$sex3=="male"|df$sex3=="female"),]
x$sex3 <- droplevels(x$sex3)
```

```{r, include=TRUE, echo=TRUE}

model1 <- lmerTest::lmer(moral_identity_symbolic ~
                    sex3
                  * age
                  + (1|country)
                , data = x
                , contrasts = list(sex3 = contr.sum, valence = contr.sum )
            )
summary(model1)
anova(model1)

# Predictors (Cultural Variables Included)

## Internalization
```{r}
x <- df[which(df$sex3=="male"|df$sex3=="female"),]
x$sex3 <- droplevels(x$sex3)
```

```{r, include=TRUE, echo=TRUE}

model1 <- lmerTest::lmer(moral_identity_internal ~
                    sex3
                    * (age
                    + Power.Distance
                    + Individualism
                    + Masculinity
                    + Uncertainty.Avoidance
                    + Long.Term.Orientation
                    + Indulgence
                    + CTL_C
                    + CTL_DS
                    + CTL_DG)
                  + (1|country)
                , data = x
                , contrasts = list(sex3 = contr.sum, valence = contr.sum )
            )
summary(model1)
anova(model1)

#### (Regular Regression)

We also ran a regression without allowing slopes to vary by country. Results are below:

```{r, include=TRUE, echo=TRUE}

fit <- lm(moral_identity_internal ~
                    sex3
                    + age
                    + Power.Distance
                    + Individualism
                    + Masculinity
                    + Uncertainty.Avoidance
                    + Long.Term.Orientation
                    + Indulgence
                    + CTL_C
                    + CTL_DS
                    + CTL_DG
                , data = x
            )

summary(fit)

## Symbolization
```{r}
x <- df[which(df$sex3=="male"|df$sex3=="female"),]
x$sex3 <- droplevels(x$sex3)
```

```{r, include=TRUE, echo=TRUE}

model1 <- lmerTest::lmer(moral_identity_symbolic ~
                    sex3
                    * (age
                    + Power.Distance
                    + Individualism
                    + Masculinity
                    + Uncertainty.Avoidance
                    + Long.Term.Orientation
                    + Indulgence
                    + CTL_C
                    + CTL_DS
                    + CTL_DG)
                  + (1|country)
                , data = x
                , contrasts = list(sex3 = contr.sum, valence = contr.sum )
            )
summary(model1)
anova(model1)

#### (Regular Regression)

We also ran a regression without allowing slopes to vary by country. Results are below:

```{r, include=TRUE, echo=TRUE}

fit <- lm(moral_identity_symbolic ~
                    sex3
                    + age
                    + Power.Distance
                    + Individualism
                    + Masculinity
                    + Uncertainty.Avoidance
                    + Long.Term.Orientation
                    + Indulgence
                    + CTL_C
                    + CTL_DS
                    + CTL_DG
                , data = x
            )

summary(fit)

# Men and Women Separately

## Men
### Internalization
```{r}
x <- df[
  which(
    df$sex3=="male"
        # |
        #   df$sex3=="female"
          ),]

x$sex3 <- droplevels(x$sex3)
```

```{r, include=TRUE, echo=TRUE}

model1 <- lmerTest::lmer(moral_identity_internal ~
                    age
                    + Power.Distance
                    + Individualism
                    + Masculinity
                    + Uncertainty.Avoidance
                    + Long.Term.Orientation
                    + Indulgence
                    + CTL_C
                    + CTL_DS
                    + CTL_DG
                  + (1|country)
                , data = x
                , contrasts = list(sex3 = contr.sum, valence = contr.sum )
            )
summary(model1)
anova(model1)
```

#### (Regular Regression)

We also ran a regression without allowing slopes to vary by country. Results are below:

```{r, include=TRUE, echo=TRUE}

fit <- lm(moral_identity_internal ~
                    age
                    + Power.Distance
                    + Individualism
                    + Masculinity
                    + Uncertainty.Avoidance
                    + Long.Term.Orientation
                    + Indulgence
                    + CTL_C
                    + CTL_DS
                    + CTL_DG
                , data = x
            )

summary(fit)

### Symbolization
```{r}
x <- df[
  which(
    df$sex3=="male"
        # |
        #   df$sex3=="female"
          ),]

x$sex3 <- droplevels(x$sex3)
```

```{r, include=TRUE, echo=TRUE}

model1 <- lmerTest::lmer(moral_identity_symbolic ~
                    age
                    + Power.Distance
                    + Individualism
                    + Masculinity
                    + Uncertainty.Avoidance
                    + Long.Term.Orientation
                    + Indulgence
                    + CTL_C
                    + CTL_DS
                    + CTL_DG
                  + (1|country)
                , data = x
                , contrasts = list(sex3 = contr.sum, valence = contr.sum )
            )
summary(model1)
anova(model1)
```

#### (Regular Regression)

We also ran a regression without allowing slopes to vary by country. Results are below:

```{r, include=TRUE, echo=TRUE}

fit <- lm(moral_identity_symbolic ~
                    age
                    + Power.Distance
                    + Individualism
                    + Masculinity
                    + Uncertainty.Avoidance
                    + Long.Term.Orientation
                    + Indulgence
                    + CTL_C
                    + CTL_DS
                    + CTL_DG
                , data = x
            )

summary(fit)

## Women
### Internalization

```{r}
x <- df[
  which(
    # df$sex3=="male"
    #     |
          df$sex3=="female"
          ),]

x$sex3 <- droplevels(x$sex3)
```

```{r, include=TRUE, echo=TRUE}

model1 <- lmerTest::lmer(moral_identity_internal ~
                    age
                    + Power.Distance
                    + Individualism
                    + Masculinity
                    + Uncertainty.Avoidance
                    + Long.Term.Orientation
                    + Indulgence
                    + CTL_C
                    + CTL_DS
                    + CTL_DG
                  + (1|country)
                , data = x
                , contrasts = list(sex3 = contr.sum, valence = contr.sum )
            )
summary(model1)
anova(model1)

#### (Regular Regression)

We also ran a regression without allowing slopes to vary by country. Results are below:

```{r, include=TRUE, echo=TRUE}

fit <- lm(moral_identity_internal ~
                    age
                    + Power.Distance
                    + Individualism
                    + Masculinity
                    + Uncertainty.Avoidance
                    + Long.Term.Orientation
                    + Indulgence
                    + CTL_C
                    + CTL_DS
                    + CTL_DG
                , data = x
            )

summary(fit)

### Symbolization
```{r}
x <- df[
  which(
    # df$sex3=="male"
    #     |
          df$sex3=="female"
          ),]

x$sex3 <- droplevels(x$sex3)
```

```{r, include=TRUE, echo=TRUE}

model1 <- lmerTest::lmer(moral_identity_symbolic ~
                    age
                    + Power.Distance
                    + Individualism
                    + Masculinity
                    + Uncertainty.Avoidance
                    + Long.Term.Orientation
                    + Indulgence
                    + CTL_C
                    + CTL_DS
                    + CTL_DG
                  + (1|country)
                , data = x
                , contrasts = list(sex3 = contr.sum, valence = contr.sum )
            )
summary(model1)
anova(model1)

#### (Regular Regression)

We also ran a regression without allowing slopes to vary by country. Results are below:

```{r, include=TRUE, echo=TRUE}

fit <- lm(moral_identity_symbolic ~
                    age
                    + Power.Distance
                    + Individualism
                    + Masculinity
                    + Uncertainty.Avoidance
                    + Long.Term.Orientation
                    + Indulgence
                    + CTL_C
                    + CTL_DS
                    + CTL_DG
                , data = x
            )

summary(fit)

>>>>

P_R <- x$`Puerto Rico`
P_R <- 
  `rownames<-`(
    `colnames<-`(
      as.data.frame(
        rbind(
          # c("mean F","SD F","mean M", "SD M", "t","df","p","d")
          # ,
          c(
            P_R$moral_identity_internal[which(P_R$sex3=="male")]
            ,"-"
            ,P_R$moral_identity_internal[which(P_R$sex3=="female")]
            ,"-"
            ,"-"
            ,"-"
            ,"-"
            ,"-"))),
      c("mean F","SD F","mean M", "SD M", "t","df","p","d"))
    ,c("Puerto Rico"))

@@

### Internalization Plot

```{r internalizationPlot}

# x <- df[which(df$sex3=="male"|df$sex3=="female"),]
# x$sex3 <- droplevels(x$sex3)
# x <- x %>% group_by(country_name) %>% do(data = (.)) %>% with( set_names(data, country_name) )
# 
# #### identify countries with small samples
# male_length <- function(x){sum(x$sex3=='male')}
# males <- lapply(x, male_length)
# female_length <- function(x){sum(x$sex3=='female')}
# females <- lapply(x, female_length)
# names(females)
# 
# #### generate a vector containing all countries with less than 10 observations for either males or females ####
# exclusions <- c(names(males[males<2]),
#   names(females[females<2]))
# 
# #### re-load ungrouped data ####
# x <- df[which(df$sex3=="male"|df$sex3=="female"),]
# x$sex3 <- droplevels(x$sex3)
# 
# # and remove missing again
# sum(is.na(x$moral_identity_internal))
# x <- x[which(is.na(x$moral_identity_internal)==FALSE),]
# 
# #### Filter out any countries to be excluded ####
# x <- subset(x, !(country_name %in% exclusions))
# 
# df1 <- x
# 
# df1_male <- df1[which(df1$sex3=="male"),]
# df1_female <- df1[which(df1$sex3=="female"),]
# 
# internal_mean_sd <- function(x){
#   z <- x
#   z$mean <- mean(z$moral_identity_internal, na.rm=T)
#   z$sd <- sd(z$moral_identity_internal, na.rm=T)
#   z
# }
# 
# 
# df1 <- rbind.data.frame(
#   internal_mean_sd(df1_female),
#   internal_mean_sd(df1_male)
# )
# 
# df1$sex3 <- dplyr::recode(df1$sex3
#                            , "male" = "Male"
#                            , "female" = "Female")
# 
# g1 <- ggplot(df1,aes(x=sex3,y=moral_identity_internal))+
#   #geom_jitter(height = .1, width = .1, size=.0001, color="gray") + 
#   geom_jitter(shape=16, position=position_jitter(height = .5, width = .45), size=.1, color="lightgrey")+
#   geom_violin(fill = NA) +
#   #ggforce::geom_sina(size=.01)+
#   # geom_sina(shape=16
#   #           , position=position_jitter(height=.25,width=0)
#   #           , size=.000001
#   #           , color="dark grey"
#   #           ,jitter_y=F
#   # )+
#   geom_boxplot(width=0.1, outlier.shape = NA, color='grey')+
#   geom_errorbar(aes(ymin=mean-sd, ymax=mean+sd), width=.06,
#                 position=position_dodge(0.05), color="#5a5a5a")+
#   stat_summary(fun=mean, geom="point", shape=16, size=.5)+
#   # stat_summary(geom = "linerange",
#   #   fun.data = mean_sdl, 
#   #   fun.args = list(mult = 1),
#   #   colour = "black"
#   # )+
#   xlab("Gender")+
#   ylab("Internalization")+  
#   facet_wrap(~df1$ISO3, ncol = 9 )+
#   #geom_jitter(shape=16, position=position_jitter(height = .5, width = .45), size=.01, color="dark grey")
#   theme_bw() +
#   theme(panel.border = element_blank(),
#         axis.line = element_line(size = .2),
#         strip.background  = element_blank(),
#         panel.grid = element_blank(),
#         plot.title=element_text(#family="Times",
#           size=12
#         ),
#         #legend.position="right",
#         legend.text=element_text(#family="Times",
#           size=8
#         ),
#         legend.title=element_text(#family="Times",
#           size=10
#         ),
#         axis.text=element_text(#family="Times",
#           colour = "black",
#           size=8
#         ),
#         axis.ticks.x = element_blank(),
#         axis.title=element_text(#family="Times",
#           size=12
#         ),
#         strip.text=element_text(#family = "Times",
#           size = 12
#         ),
#         # strip.background = element_rect(fill = "white"),
#         legend.position="none")
# 
# ggsave("plots/internalization.png", g1, width = 40, height = 25, units = "in", dpi = 300)

```{r, InternalizationGender,fig.cap="Gender differences in Internalization for each country",include=TRUE}
#suppressWarnings(print(g1))

<style>
#wrapper { width: 100%;; height: 702px; padding: 0; overflow: hidden; border: 1px}
#scaled-frame { width: 250%; height: 900px; border: 1px; }
#scaled-frame {
    zoom: 0.50;
    -moz-transform: scale(0.50);
    -moz-transform-origin: 0 0;
    -o-transform: scale(0.50);
    -o-transform-origin: 0 0;
    -webkit-transform: scale(0.50);
    -webkit-transform-origin: 0 0;
}

@media screen and (-webkit-min-device-pixel-ratio:0) {
 #scaled-frame  { zoom: 1;  }
}
</style>

<div id="wrapper"><iframe id="scaled-frame" src="plots/internalization.png"></iframe></div>

@@

rownames(test) <-  unlist(lapply(1:length(rownames(test)), loop_exclusions_fun))
test
#test <-
test[order(rownames(test) ),]

@@

P_R <- x$`Puerto Rico`
P_R <- 
  `rownames<-`(
    `colnames<-`(
      as.data.frame(
        rbind(
          # c("mean F","SD F","mean M", "SD M", "t","df","p","d")
          # ,
          c(
            P_R$moral_identity_symbolic[which(P_R$sex3=="male")]
            ,"-"
            ,P_R$moral_identity_symbolic[which(P_R$sex3=="female")]
            ,"-"
            ,"-"
            ,"-"
            ,"-"
            ,"-"))),
      c("mean F","SD F","mean M", "SD M", "t","df","p","d"))
    ,c("Puerto Rico"))

@@

### Symbolization Plot

```{r symbolizationPlot}

# x <- df[which(df$sex3=="male"|df$sex3=="female"),]
# x$sex3 <- droplevels(x$sex3)
# x <- x %>% group_by(country_name) %>% do(data = (.)) %>% with( set_names(data, country_name) )
# 
# #### identify countries with small samples
# male_length <- function(x){sum(x$sex3=='male')}
# males <- lapply(x, male_length)
# female_length <- function(x){sum(x$sex3=='female')}
# females <- lapply(x, female_length)
# names(females)
# 
# #### generate a vector containing all countries with less than 10 observations for either males or females ####
# exclusions <- c(names(males[males<2]),
#   names(females[females<2]))
# 
# #### re-load ungrouped data ####
# x <- df[which(df$sex3=="male"|df$sex3=="female"),]
# x$sex3 <- droplevels(x$sex3)
# 
# # and remove missing again
# sum(is.na(x$moral_identity_symbolic))
# x <- x[which(is.na(x$moral_identity_symbolic)==FALSE),]
# 
# #### Filter out any countries to be excluded ####
# x <- subset(x, !(country_name %in% exclusions))
# 
# df1 <- x
# 
# df1_male <- df1[which(df1$sex3=="male"),]
# df1_female <- df1[which(df1$sex3=="female"),]
# 
# internal_mean_sd <- function(x){
#   z <- x
#   z$mean <- mean(z$moral_identity_symbolic, na.rm=T)
#   z$sd <- sd(z$moral_identity_symbolic, na.rm=T)
#   z
# }
# 
# 
# df1 <- rbind.data.frame(
#   internal_mean_sd(df1_female),
#   internal_mean_sd(df1_male)
# )
# 
# df1$sex3 <- dplyr::recode(df1$sex3
#                            , "male" = "Male"
#                            , "female" = "Female")
# 
# g1 <- ggplot(df1,aes(x=sex3,y=moral_identity_symbolic))+
#   geom_jitter(height = .1, width = .1, size=.0001, color="gray") +
#   geom_jitter(shape=16, position=position_jitter(height = .5, width = .45), size=.001, color="lightgrey")+
#   geom_violin(fill = NA) +
#   #ggforce::geom_sina(size=.01)+
#   # geom_sina(shape=16
#   #           , position=position_jitter(height=.25,width=0)
#   #           , size=.000001
#   #           , color="dark grey"
#   #           ,jitter_y=F
#   # )+
#   geom_boxplot(width=0.1, outlier.shape = NA, color='grey')+
#   geom_errorbar(aes(ymin=mean-sd, ymax=mean+sd), width=.06,
#                 position=position_dodge(0.05), color="#5a5a5a")+
#   stat_summary(fun=mean, geom="point", shape=16, size=.5)+
#   # stat_summary(geom = "linerange",
#   #   fun.data = mean_sdl,
#   #   fun.args = list(mult = 1),
#   #   colour = "black"
#   # )+
#   xlab("Gender")+
#   ylab("Internalization")+
#   facet_wrap(~df1$ISO3, ncol = 9 )+
#   #geom_jitter(shape=16, position=position_jitter(height = .5, width = .45), size=.01, color="dark grey")
#   theme_bw() +
#   theme(panel.border = element_blank(),
#         axis.line = element_line(size = .2),
#         strip.background  = element_blank(),
#         panel.grid = element_blank(),
#         plot.title=element_text(#family="Times",
#           size=12
#         ),
#         #legend.position="right",
#         legend.text=element_text(#family="Times",
#           size=8
#         ),
#         legend.title=element_text(#family="Times",
#           size=10
#         ),
#         axis.text=element_text(#family="Times",
#           colour = "black",
#           size=8
#         ),
#         axis.ticks.x = element_blank(),
#         axis.title=element_text(#family="Times",
#           size=12
#         ),
#         strip.text=element_text(#family = "Times",
#           size = 12
#         ),
#         # strip.background = element_rect(fill = "white"),
#         legend.position="none")

#g1

#ggsave("plots/symbolization.png", g1, width = 40, height = 25, units = "in", dpi = 300)
#g2
```

```{r, SymbolizationGender,fig.cap="Gender differences in Symbolization for each country",include=TRUE}
#suppressWarnings(print(g1))

@@

<style>
#wrapper { width: 100%;; height: 702px; padding: 0; overflow: hidden; border: 1px}
#scaled-frame { width: 250%; height: 900px; border: 1px; }
#scaled-frame {
    zoom: 0.50;
    -moz-transform: scale(0.50);
    -moz-transform-origin: 0 0;
    -o-transform: scale(0.50);
    -o-transform-origin: 0 0;
    -webkit-transform: scale(0.50);
    -webkit-transform-origin: 0 0;
}

@media screen and (-webkit-min-device-pixel-ratio:0) {
 #scaled-frame  { zoom: 1;  }
}
</style>

<div id="wrapper"><iframe id="scaled-frame" src="plots/internalization.png"></iframe></div>
